\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-06 trunk/europa-basics.tex
updates

A predicate defines a relation between objects and properties. In
\eu, we define such relations between variables whose domains are
sets of objects and sets of properties. For example, we might use a
predicate Pointing(a,p) to indicate that a rover's attitude controller
a is pointing at position p. Note that a is a variable which may have
a number of possible values in a problem with multiple
satellites. Similarly, p is a variable whose values are the set of
possible positions. In a grounded plan, single values will be
specified for each variable as we saw in the case of a solved
Constraint Satisfaction Problem.

In general, is is not sufficient to state that a predicate is true
without giving it some temporal extent over which it holds. Predicates
that are always true can be thought to hold from the beginning to the
end of time. However, in practice, the temporal extent of interest
must be defined with timepoints to represent its start and end. So we
might want to write Pointing(a,s,e,p) to indicate that the attitude
controller a is pointing at position p from time s to time e. In fact,
this pattern of using such predicates to describe both state and
behavior of objects is so prevalent in \eu that we have introduced
a special construct called a Token which has the built in variables to
indicate the object to which the statement principally applies and the
timepoints over which it holds. In \eu, all predicate instances are
Tokens.

>>>>

A predicate defines a relation between objects and properties. In \eu,
we define such relations between variables whose domains are sets of
objects and sets of properties. For example, we might use a predicate
\texttt{Pointing($a,p$)} to indicate that a rover's attitude controller
$a$ is pointing at position $p$. Note that $a$ is a variable which may
have a number of possible values in a problem with multiple
satellites. Similarly, $p$ is a variable whose values are the set of
possible positions. In a grounded plan, single values will be
specified for each variable as we saw in the case of a solved
Constraint Satisfaction Problem.

In general, it is not sufficient to state that a predicate is true
without giving it some temporal extent over which it holds. Predicates
that are always true can be thought to hold from the beginning to the
end of time. However, in practice, the temporal extent of interest
must be defined with timepoints to represent its start and end. So we
might want to write \texttt{Pointing($a,s,e,p$)} to indicate that the
attitude controller a is pointing at position $p$ from time $s$ to
time $e$. In fact, this pattern of using such predicates to describe
both state and behavior of objects is so prevalent in \eu that we have
introduced a special construct called a Token which has the built in
variables to indicate the object to which the statement principally
applies and the timepoints over which it holds. In \eu, all predicate
instances are Tokens.
